---
title: "lodestar_start_guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lodestar_start_guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(gwangmyeongseong3)
```

### Best practises and hiding passwords and usernames

In this vignette we will be exploring the `Lodestar` software for sequence
annotation and comparative genomics. In the canonical code examples included
we will be connecting to a database server that uses a username and password
that I would prefer not to be shown in a public-facing technical document. 

The `Lodestar` software uses the [r-lib/keyring](https://github.com/r-lib/keyring) 
package to cache and encrypt username::password pairs that are associated with
a given RDBMS and database instance. 

The`keyring` works out of the box on Windows and MacOS - if you are using a Linux
computer please ensure that e.g. `libsecret-1-dev` has been installed on your
system.


```{r keyring_intro, message=FALSE}
# define the objects required for the key ...
RDBMS <- "dummy_psql" 
database <- "lodestar_drosophila"
username <- "dr_evil"
password <- "topsecret"

# define the key object - this will be saved in ~/.config/r-keyring
creds <- lodestar_creds(
  username=username, password=password, 
  service=database, keyring=RDBMS)

# let's see what has been saved in the keychain
creds$keyring_is_locked(RDBMS)
creds$list(keyring = RDBMS, service=database)

# and show how the password can be extracted again ...
creds$get(keyring = RDBMS, service=database, username=username)

# delete this keyring
creds$keyring_delete(RDBMS)
```

Users working with simple installations should only need to define a simple
`lodestar_creds` configuration once; other steps within this *Vignette* will
automatically pick up these config facets.

## Connecting to a PostgreSQL database server

On this development and documentation server, I am running a `Postgres` server.
The installation defines a user, *`stephen`* who with the appropriate password
is allowed to connect to an exemplar database called *`lodestar`*.

```{r dbconnecion, message=FALSE}
lsconn <- LodestarConn$new()
conn <- lsconn$connection()
print(conn)

```

```{r cli_demo}
clist = c("a", "b", "c")
cli::cli_alert_success("Downloaded {length(clist)} packages")
```
