---
title: "lodestar_start_guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lodestar_start_guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(gwangmyeongseong3)
```

### Best practises and hiding passwords and usernames

In this vignette we will be exploring the `Lodestar` software for sequence
annotation and comparative genomics. In the canonical code examples included
we will be connecting to a database server that uses a username and password
that I would prefer not to be shown in a public-facing technical document. We
will therefore have a quick introduction to the 
[r-lib/keyring](https://github.com/r-lib/keyring) software.

`keyring` works out of the box on Windows and MacOS - if you are using a Linux
computer please ensure that e.g. `libsecret-1-dev` has been installed on your
system.


```{r keyring_intro}
# define the objects required for the key ...
keychain_name <- "my_credentials"
kr_service <- "my_service"
kr_username <- "my_username"
kr_password <- "topsecret"

# define the key object - this will be saved in ~/.config/r-keyring
kb <- keyring::backend_file$new()

# create the keyring (this will be placed in the object above)
kb$keyring_create(keychain_name)

# and set the username, password and service parameters to be stored
kb$set_with_value(service=kr_service, username=kr_username, password=kr_password, keyring=keychain_name)

# let's see what has been saved in the keychain
kb$keyring_is_locked(keychain_name)
kb$keyring_list()
kb$list(keyring = keychain_name, service=kr_service)

# and show how the password can be extracted again ...
kb$get(keyring = keychain_name, service=kr_service, username=kr_username)

# delete this keyring
kb$keyring_delete(keychain_name)
```


### Using passwords in Lodestar

The `Lodestar` package provides a simple method to set the passwords that will
be used for connecting to one or more databases.

```{r lodestar_creds} 
creds <- lodestar_creds(username=kr_username, password=kr_password, service=kr_service, keyring=keychain_name)
creds$list(keyring = keychain_name, service=kr_service)
```


